Plots for Latent Hawkes Paper

### 2020-07-22 output_scripts/Paper_Plots.Rmd
run the same cohort for all plots, and some small changes to correct some plots

```{r fig-2a-contour-plot}
current_cohort <- 1
#png(paste(plot_path,"contour.png",sep=""),width=480,height=480)
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
z.func <- function(x,y){
  return(x*y*eta1_mean*exp(-eta2_mean*abs(x-y))/(1+exp(-eta3_mean*(y-x))))
  # this is because axes are flipped that we have y-x in last term
  #return(x*y*eta1_mean/(1+exp(eta2_mean*abs(x-y)-eta3_mean*(y-x))))
}
z_plot <- outer(seq(1,0,-0.01),  
                seq(0,1,0.01), 
                z.func)
my.image.plot(seq(0,1,0.01), seq(0,1,0.01), z_plot,
              xlab=expression(f[j]),ylab=expression(f[i]),
              my.main="(a)", cex.main=2.3, 
              cex.lab=2.5, xLabels=c(1,0), yLabels=c(0,1))

@@

```{r fig-2b-diag-plot,echo=FALSE,warning=FALSE}
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
f_est <- apply(sim_cohort_hp$f,2,mean)
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
                   observe=list(observe.id),
                   observe.length=list(observe.time),
                   no.events=list(no.events))
unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])

@@

```{r fig-3a-baseline-rate}
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
gamma_mean <- apply(sim_cohort_dchp$gamma,2,mean)
zeta_mean <- apply(sim_cohort_dchp$zeta,2,mean)

@@

# png(paste(plot_path,"/lambda0_",cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
matrixPlotParameter(latent_social_matrix[rev(expert_rank_10[[current_cohort]]),expert_rank_10[[current_cohort]]],
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),title="(a)")
# mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
#       at=1/17.8*seq(2,12,2)+0.09)
#dev.off()
```
## Figure 3b: Ranking Comparison

```{r fig-3b-rank-comparison}
current_cohort <- 1
colors_plot <- viridis(2)
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
# png(paste(plot_path,"/rank_",cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
par(oma = c(0,0,2,0), mar = c(3,4,1,1),mgp=c(0,0.5,0))
plot(order(expert_rank_10[[current_cohort]]),
     apply(sim_cohort_hp$f,2,mean),pch=16,cex=1.2,
     #col= "steelblue",
     col = colors_plot[1],
     ylab="",xlab="",
     xlim=c(1,12.5),ylim=c(0,1), xaxt="n", yaxt="n")
segments(order(expert_rank_10[[current_cohort]]),
         apply(sim_cohort_hp$f,2,mean)-apply(sim_cohort_hp$f,2,sd),
         order(expert_rank_10[[current_cohort]]),
         apply(sim_cohort_hp$f,2,mean)+apply(sim_cohort_hp$f,2,sd),
         #col= add.alpha("steelblue",0.8),lwd=2)
         col = add.alpha(colors_plot[1],0.8), lwd =2)
points(order(expert_rank_10[[current_cohort]])+0.2,
       apply(sim_cohort_dchp$f,2,mean),
       pch=16,cex=1.2,
       col=colors_plot[2])
       #col="goldenrod2")
segments(order(expert_rank_10[[current_cohort]])+0.2,
         apply(sim_cohort_dchp$f,2,mean)-apply(sim_cohort_dchp$f,2,sd),
         order(expert_rank_10[[current_cohort]])+0.2,
         apply(sim_cohort_dchp$f,2,mean)+apply(sim_cohort_dchp$f,2,sd),
         col= add.alpha(colors_plot[2],0.8),lwd=2)
         #col= add.alpha("goldenrod2",0.8),lwd=2)

axis(BELOW<-1, at=1:12, labels=expert_rank_10[[current_cohort]], cex.axis=1.3, tck=-0.015)
mtext(text=11, side=1, line=0.5, cex=1.3, at=6)

@@

```{r fig4b-recover-latent-states}
y.ub <- c(130,72,31)
#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
model_colors <- viridis::viridis(3)
layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 200#130
my.long.x <- 205#134.5
legend.x <- c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
# negative.col <- add.alpha('lightskyblue',0.6)
# positive.col <- add.alpha('tomato',0.6)
negative.col <- viridis::viridis(5,alpha = 0.6)[1]
positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

@@

```{r fig5-residual-ks}
cols_plot <- viridis::viridis(4)
#load("../output/sim_model3_fit123_residuals.RData")
par(mfrow=c(5,5),mar=rep(0.2,4),oma=c(2.4,2.4,0.5,0.5))
for(i in c(5:1)){
  for(j in c(5:1)){
    if(i==j){
      plot(1,1,type="n",xlim=c(0,1),ylim=c(0,1),
           bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
      if(i==5){
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04,col=cols_plot[1],border=NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.22,col=cols_plot[2],border=NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.44,col=cols_plot[3],border=NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.66,col=cols_plot[4],border=NA)
        text(c(0.43,0.58,0.61,0.4),seq(0.8,0.14,-0.22),
             c("C-HP", "C-DCHP", "C-MMHP", "True"),
             cex=1.7)
      }
    }else{
      # PR <- c((N_array-Lambda_model1_array)[,i,j],(N_array-Lambda_model2_array)[,i,j],
      #         (N_array-Lambda_model3_array)[,i,j],(N_array-Lambda_true_array)[,i,j])
      PR <- c(KS_model1_array[,i,j],KS_model2_array[,i,j],
              KS_model3_array[,i,j],KS_true_array[,i,j])
      Type <- c(rep(1,n_sim),rep(2,n_sim),rep(3,n_sim),rep(4,n_sim))
      boxplot(PR ~ Type,  
              col = cols_plot,
              #col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),   
              xlab="",ylab="",xaxt="n",yaxt="n")#names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
    }
  }
}
mtext(text=c(1:5), side=2, line=0.5, outer=TRUE, cex=2, las=2,
      at=c(0:4)/5+0.1)
mtext(text=c(1:5), side=1, line=1, outer=TRUE, cex=2,
      at=c(0:4)/5+0.1)

@@

```{r fig-7-prMatrix-Cohort1}
current_cohort <- 1

@@

```{r fig-8a-frob-norm-cohort1}
load("../output/plot_N_predict.RData")
current_cohort <- 5# cohort 1 looks worse than rest

@@

```{r construct data for plot, results='hide',message=FALSE,cache=TRUE}
library(PlayerRatings)

current_cohort <- 1

@@

# ---------------- simulation mean and sd
sim_gl_array <- array(NA, dim=c(12,testing_end-training_end+1,100))
for(s in 1:100){
  print(s)
  temp_gl <- glickoScoreSimulationWithWindowsReturnAll(
    predict.sim = m3_predict_sim[5:8,s],
    history.df = glick.df[1:training_end,])
  history_matrix <- temp_gl$history[,,1]

  if(testing_end>ncol(temp_gl$history[,,1])){
    history_matrix <- cbind(history_matrix,
                            t(matrix(rep(history_matrix[,ncol(history_matrix)],
                                         testing_end-ncol(temp_gl$history[,,1])),
                                     nrow=testing_end-ncol(temp_gl$history[,,1]),
                                     byrow=TRUE)))
  }else{
    try(
    history_matrix <- temp_gl[,1:testing_end]
    )
  }
  sim_gl_array[,,s] <- history_matrix[,training_end:testing_end]
}
```

@@

```{r process for state separation cohort1,eval=FALSE}
# only run this once and save the results
# this doesn't need to be rerun ever, even if the stan fits change
load(paste(data_path,cohort_names[current_cohort],
             "/cmmhp_est_zt_",cohort_names[current_cohort],
             ".RData",sep=''))
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
                   observe=list(observe.id),
                   observe.length=list(observe.time),
                   no.events=list(no.events))
unique_observe_win <- unique(return_df[,c("day","observe.id","observe.time")])

@@

```{r process data for plot 10b}
library(PlayerRatings)
current_cohort <- 1
load(paste(data_path,cohort_names[current_cohort],
           "/dsnl_poisson_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/dsnl_state_separation_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
sub.types <- c("All", "Active", "Inactive"); # three methods
task.types <- paste0("day", 1:21);

>>>>

```{r fig-2a-contour-plot}
current_cohort <- 5
#png(paste(plot_path,"contour.png",sep=""),width=480,height=480)
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
z.func <- function(x,y){
  return(x*y*eta1_mean*exp(-eta2_mean*abs(x-y))/(1+exp(-eta3_mean*(y-x))))
  # this is because axes are flipped that we have y-x in last term
  #return(x*y*eta1_mean/(1+exp(eta2_mean*abs(x-y)-eta3_mean*(y-x))))
}
z_plot <- outer(seq(1,0,-0.01),  
                seq(0,1,0.01), 
                z.func)
my.image.plot(seq(0,1,0.01), seq(0,1,0.01), z_plot,
              xlab=expression(f[j]),ylab=expression(f[i]),
              my.main="(a)", cex.main=2.3, 
              cex.lab=2.5, xLabels=c(1,0), yLabels=c(0,1))

@@

```{r fig-2b-diag-plot,echo=FALSE,warning=FALSE}
current_cohort <- 5

load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
f_est <- apply(sim_cohort_hp$f,2,mean)
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
                   observe=list(observe.id),
                   observe.length=list(observe.time),
                   no.events=list(no.events))
unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])

@@

```{r fig-3a-baseline-rate}
current_cohort <- 5

load(paste(data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
gamma_mean <- apply(sim_cohort_dchp$gamma,2,mean)
zeta_mean <- apply(sim_cohort_dchp$zeta,2,mean)

@@

# png(paste(plot_path,"/lambda0_",cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
matrixPlotParameter(latent_social_matrix[rev(expert_rank_10[[current_cohort]]),
                                         expert_rank_10[[current_cohort]]],
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]),title="(a)")
# mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
#       at=1/17.8*seq(2,12,2)+0.09)
#dev.off()
```
## Figure 3b: Ranking Comparison

```{r fig-3b-rank-comparison}
current_cohort <- 5

colors_plot <- viridis(2)
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
# png(paste(plot_path,"/rank_",cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
par(oma = c(0,0,2,0), mar = c(3,4,1,1),mgp=c(0,0.5,0))
plot(order(expert_rank_10[[current_cohort]]),
     apply(sim_cohort_hp$f,2,mean),pch=16,cex=1.2,
     #col= "steelblue",
     col = colors_plot[1],
     ylab="",xlab="",
     xlim=c(1,12.5),ylim=c(0,1), xaxt="n", yaxt="n")
segments(order(expert_rank_10[[current_cohort]]),
         apply(sim_cohort_hp$f,2,mean)-apply(sim_cohort_hp$f,2,sd),
         order(expert_rank_10[[current_cohort]]),
         apply(sim_cohort_hp$f,2,mean)+apply(sim_cohort_hp$f,2,sd),
         #col= add.alpha("steelblue",0.8),lwd=2)
         col = add.alpha(colors_plot[1],0.8), lwd =2)
points(order(expert_rank_10[[current_cohort]])+0.2,
       apply(sim_cohort_dchp$f,2,mean),
       pch=16,cex=1.2,
       col=colors_plot[2])
       #col="goldenrod2")
segments(order(expert_rank_10[[current_cohort]])+0.2,
         apply(sim_cohort_dchp$f,2,mean)-apply(sim_cohort_dchp$f,2,sd),
         order(expert_rank_10[[current_cohort]])+0.2,
         apply(sim_cohort_dchp$f,2,mean)+apply(sim_cohort_dchp$f,2,sd),
         col= add.alpha(colors_plot[2],0.8),lwd=2)
         #col= add.alpha("goldenrod2",0.8),lwd=2)

axis(BELOW<-1, at=1:12, labels=expert_rank_10[[current_cohort]], cex.axis=1.3, tck=-0.015)
#mtext(text=11, side=1, line=0.5, cex=1.3, at=6)

@@

```{r fig4b-recover-latent-states}
y.ub <- c(130,72,31)
#model_colors <- c("steelblue", "goldenrod2", "firebrick2")
model_colors <- viridis::viridis(3)
layout(matrix(c(1:6), 6, 1), heights=rep(c(2.5,1),3))
layout(matrix(c(1:6), 6, 1), heights=rep(c(7.5,1),3))
my.xlim <- 200#130
my.long.x <- 205#134.5
legend.x <- c(135,135,135)
legend.y <- #c(34,32,32)
legend.y <- c(62,37,18)#c(22,22,22)
legend.cex <- 1.5 #3
line.alpha <- c(0.9,0.6)
line.wdth <- c(2,2.5)
negative.col <- add.alpha('lightskyblue',0.6)
positive.col <- add.alpha('tomato',0.6)
#negative.col <- viridis::viridis(5,alpha = 0.6)[1]
#positive.col <- viridis::viridis(5,alpha = 0.6)[4]
par(mar = c(0,0.3,0,0.1), oma = c(3,3.5,4,0),
    tcl=0.2,mgp=c(0.5,0,0), xpd=TRUE)

@@

```{r fig5-residual-ks, fig.height=7}
cols_plot <- viridis::viridis(4)
#load("../output/sim_model3_fit123_residuals.RData")
par(mfrow=c(5,5),mar=rep(0.2,4),oma=c(2.4,2.4,0.5,0.5))
for(i in c(5:1)){
  for(j in c(5:1)){
    if(i==j){
      plot(1,1,type="n",xlim=c(0,1),ylim=c(0,1),
           bty="n", xlab="",ylab="",xaxt="n",yaxt="n",axes=FALSE)
      if(i==5){
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04,col=cols_plot[1],border=NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.22,col=cols_plot[2],border=NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.44,col=cols_plot[3],border=NA)
        polygon(c(0,0,0.15,0.15),c(0.72,0.8,0.8,0.72)+0.04-0.66,col=cols_plot[4],border=NA)
        text(c(0.43,0.58,0.61,0.4),seq(0.8,0.14,-0.22),
             c("C-HP", "C-DCHP", "C-MMHP", "True"),
             cex=1.7)
      }
    }else{
      # PR <- c((N_array-Lambda_model1_array)[,i,j],(N_array-Lambda_model2_array)[,i,j],
      #         (N_array-Lambda_model3_array)[,i,j],(N_array-Lambda_true_array)[,i,j])
      PR <- c(KS_model1_array[,i,j],KS_model2_array[,i,j],
              KS_model3_array[,i,j],KS_true_array[,i,j])
      Type <- c(rep(1,n_sim),rep(2,n_sim),rep(3,n_sim),rep(4,n_sim))
      boxplot(PR ~ Type,  
              col = cols_plot,
              #col = c("steelblue", "goldenrod2", "firebrick2", "chartreuse3"),   
              xlab="",ylab="",xaxt="n",yaxt="n")#names = c("C-HP", "C-HP-DC", "C-MMHP", "True")
    }
  }
}
mtext(text=c(1:5), side=2, line=0.5, outer=TRUE, cex=2, las=2,
      at=c(0:4)/5+0.1)
mtext(text=c(5:1), side=1, line=1, outer=TRUE, cex=2,
      at=c(0:4)/5+0.1)

@@

```{r fig-7-prMatrix-Cohort5, fig.height=7}
current_cohort <- 5

@@

```{r fig-8a-frob-norm-cohort5}
load("../output/plot_N_predict.RData")
current_cohort <- 5# cohort 1 looks worse than rest

@@

```{r construct data for plot, results='hide',message=FALSE,cache=FALSE}
library(PlayerRatings)

current_cohort <- 5

@@

# ---------------- simulation mean and sd
sim_gl_array <- array(NA, dim=c(12,testing_end-training_end+1,1000))
for(s in 1:1000){
  print(s)
  temp_gl <- glickoScoreSimulationWithWindowsReturnAll(
    predict.sim = m3_predict_sim[5:8,s], #7 for c 2 and 10
    history.df = glick.df[1:training_end,])
  history_matrix <- temp_gl$history[,,1]

  if(testing_end>ncol(temp_gl$history[,,1])){
    history_matrix <- cbind(history_matrix,
                            t(matrix(rep(history_matrix[,ncol(history_matrix)],
                                         testing_end-ncol(temp_gl$history[,,1])),
                                     nrow=testing_end-ncol(temp_gl$history[,,1]),
                                     byrow=TRUE)))
  }else{
    # this line makes no sense, and should likely never happen
    # try(
    history_matrix <- history_matrix[,1:testing_end]#temp_gl$history[,1:testing_end]
    # )
  }
  sim_gl_array[,,s] <- history_matrix[,training_end:testing_end]
}
```

@@

```{r process for state separation cohort1,eval=FALSE}
# only run this once and save the results
# this doesn't need to be rerun ever, even if the stan fits change
current_cohort <- 5

load(paste(data_path,cohort_names[current_cohort],
             "/cmmhp_est_zt_",cohort_names[current_cohort],
             ".RData",sep=''))
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
                   observe=list(observe.id),
                   observe.length=list(observe.time),
                   no.events=list(no.events))
unique_observe_win <- unique(return_df[,c("day","observe.id","observe.time")])

@@

```{r process data for plot 10b}
library(PlayerRatings)
current_cohort <- 5
load(paste(data_path,cohort_names[current_cohort],
           "/dsnl_poisson_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/dsnl_state_separation_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
sub.types <- c("All", "Active", "Inactive"); # three methods
task.types <- paste0("day", 1:21);
